Codebook created on 2025-05-21 at 2025-05-21 15:18:06

### 2025-05-21 codebook_data.Rmd
data

---
title: "Codebook created on 2025-04-22 at 2025-04-22 14:41:32"
output: github_document
---

@@

## Dataset description
The data contains 1000 cases and 28 variables.

@@

```{r}
summaries <- read.csv("codebook_data_simulated.csv", stringsAsFactors = FALSE)
summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]
options(knitr.kable.NA = '')
knitr::kable(summaries, row.names = FALSE, digits = 2)
```

>>>>

---
title: "Codebook created on 2025-05-21 at 2025-05-21 15:18:06"
output: github_document
---

@@

## Dataset description
The data contains 634 cases and 28 variables.

@@

```{r}
summaries <- read.csv("codebook_data.csv", stringsAsFactors = FALSE)
summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]
options(knitr.kable.NA = '')
knitr::kable(summaries, row.names = FALSE, digits = 2)
```
